### 2014-05-13 tex/main-body-text.tex
minor results added

\subsection*{Results} 
Run times were relatively short. The six groups of runs for the default settings 
averaged 188.8 minutes (1.5 min SD). While no  plateaus were observed in any of the six groups for a \textit{k} greater than two, the plateau record varied greatly among each group for \textit{k}=2 (plateau 
sequences- Run1= 3,2,3,5,2,4; Run2=2,5,2,3,2,3; Run3=2,2,2,2,2,5; Run4=2,3,4,2,2,2,3; Run5=2,2,2,4,3,2; 
and; Run6=2,3,3,4,2,2,5,2). The plateau analysis procedure suggested by \citet{Duc&Tur2012} leads to 
an \textit{undecided} estimate of K as a consequence of no plateau lengths being greater than 6. Despite 
the K estimation based on rules of thumb devloped by \citet{Duc&Tur2012}, Distruct plots for each group of runs 
for \textit{k}=2-4 lead to nearly identical clustering of individuals (See supplementary materials). While only two of the six 'best runs' when \textit{k}=2 ended with identical clustering (same mean LLOD score), all other runs differed by at most the allocation of 13 individuals. When \textit{k} was set to three and four all runs provided very similar clustering.

>>>>

\subsection*{Results} 
Run times were relatively short for both programs. The six groups of runs for {\sc flock} 
using the default settings required 1133 minutes to complete. Each individual group  of runs 
averaged 188.8 minutes (1.5 min SD). The six iterations of {\sc structure} completed in 
XXXX minutes with each iterations averaging XXXX (SD).

While no  plateaus were observed in any of the six groups for a \textit{k} greater than 
two, the plateau record varied greatly among each
 group for \textit{k}=2 (plateau  sequences- Run1= 3,2,3,7,4; Run2=2,5,2,3,2,3; Run3=2,2,2,2,2,5; 
Run4=2,3,4,2,4,3; Run5=2,2,5,5,3; and; Run6=2,2,2,2,2,3,3). The plateau analysis 
procedure suggested by \citet{Duc&Tur2012} leads to 
either an estimate of K$\geq$2 or \textit{undecided} as a consequence of no plateau 
lengths being greater than 6. Distruct plots for each group of runs for \textit{k}=2-4 
lead to nearly identical clustering of individuals (See supplementary materials). While 
only two of the six 'best runs' when 
\textit{k}=2 ended with identical clustering (same mean LLOD score), all other runs 
differed by at most the allocation of 13 individuals. When \textit{k} was set to three 
and four all runs provided very similar clustering.
